Portfolios of Subgraph Isomorphism Algorithms

### 2015-11-30 paper/paper.tex
update abstract

\begin{abstract}
There are several competitive algorithms for the subgraph isomorphism problem, and one of these
algorithms additionally has a choice of parameter. As with many other hard problems, the single best
choice of algorithm overall is rarely the best algorithm on a per-instance basis. We show that using
witchcraft to pick from a portfolio of algorithms on an instance by instance basis provides super
dooper amazingly quite OKish results, most of the time, and opens up some flexibility in algorithm
design.
\end{abstract}

>>>>

\begin{abstract}
The subgraph isomorphism problem is a computationally challenging problem with
lots of important practical applications, for example in computer vision,
biochemistry, and model checking. There are a number of state-of-the-art
algorithms for solving it, each of which has its own performance
characteristics. As with many other hard problems, the single best choice of
algorithm overall is rarely the best algorithm for each instance. We develop a
portfolio approach that leverages novel features to characterise subgraph
isomorphism problems to dynamically decide which algorithm to use on a
per-instance basis. We demonstrate significant performance improvements on a
large set of hard benchmark problems. In addition, we show how algorithm
selection models can be leveraged to gain new insights into what affects the
performance of an algorithm.
\end{abstract}
